### 2022-05-03 README.Rmd
CRAN 1.5.0 release ready.

# test of no treatment effect
lhs <- matrix(c(1, -1, 0, 0,
                0, 1, -1, 0,
                0, 0, 1, -1), byrow = TRUE, nrow = 3)
lht(fit3, lhs)
```

>>>>

# test of no treatment effect
lhs <- matrix(c(1, -1, 0, 0,
                0, 1, -1, 0,
                0, 0, 1, -1), byrow = TRUE, nrow = 3)
lht(fit3, lhs = lhs)

# logistic regression
fit4 <- el_glm(vs ~ mpg, data = mtcars, family = binomial)
summary(fit4)
```
